### 2021-12-15 thesis/tex/conclusion.tex
update, and removed files

\chapter{Conclusion}\label{ch:conc}
In this thesis, we have explored the potential of explaining new physics using detectors handled by the IceCube collaboration.
We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. 
We mentioned the Super-Kamiokande experiment and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}, in direct violation of the Standard Model. 
We saw that, by adding a right-handed neutrino field, neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
In Sec.~\ref{ch:oscillation}, we saw how the neutrino mixing matrix could be constructed and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures. Adding a term for matter potential,
we then arrived at a Hamiltonian that we used in the time-dependent Schrödinger equation to solve for the oscillation probabilities in matter.

>>>>

\chapter{Conclusion}\label{ch:conc}
In this thesis, we have explored the potential of explaining new physics using detectors handled by the IceCube collaboration.
We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. 
We mentioned the Super-Kamiokande experiment and that their 1998 result found no other explanation than that $\nm$ oscillated~\cite{sk1998}, in direct violation of the Standard Model. 
We saw that, by adding a right-handed neutrino field, neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
In Sec.~\ref{ch:oscillation}, we saw how the neutrino mixing matrix could be constructed and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures. Adding a term for matter potential,
we then arrived at a Hamiltonian that we used in the time-dependent Schrödinger equation to solve for the oscillation probabilities in matter.
